Global patterns of forest autotrophic carbon fluxes

### 2020-02-21 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

The effects of climate and latitude on FACF were analysed using mixed effects models using the package 'lme4' [@bates_fitting_2015] in R v.3.5.1 [@r_core_team_r:_2018]. First, the individual effect of each climate variable on each flux variable was modelled by specifying the climate variable as a fixed effect in a univariate model. For each climate variable, three models were specified: a null model; a model with the climate variable as a linear term; and a model with the climate variable as a second-order polynomial term. AIC values were calculated for the models and used to select the best model. If the best model included a polynomial term, the shape of the polynomial relationship was considered. If the shape of the relationship *made biological sense*, and was a significant improvement on the linear relationship (deltaAIC >2), we accepted the polynomial as the best model. If not, we ran the linear model as the final model. $R^2$ values were calculated for the best model. All $R^2$ values presented here are marginal $R^2$ values, and refer to the proportion of variation explained by only the fixed effects, unless otherwise specified. In addition, slope coefficients were calculated for the linear models.

@@

For the variables which showed a significant interactive or additive effect between MAT and MAP, no other climate variable, in combination with MAT, significantly improved on that model. For NPP, there was a significant interactive effect between MAT and water stress months, with this model explaining nearly 5% more variation in NPP than MAT alone {**Helene: but less than MATxMAP? if so, why bother mentioning?**}. However, for ANPP~foliage~, no multivariate model improved on the univariate model including only MAT.

>>>>

The effects of climate and latitude on FACF were analysed using mixed effects models using the package 'lme4' [@bates_fitting_2015] in R v.3.5.1 [@r_core_team_r:_2018]. First, the individual effect of each climate variable on each flux variable was modelled by specifying the climate variable as a fixed effect in a univariate model. For each climate variable, three models were specified: a null model; a model with the climate variable as a linear term; and a model with the climate variable as a second-order polynomial term. AIC values were calculated for the models and used to select the best model. If the best model included a polynomial term, the shape of the polynomial relationship was considered. If the shape of the relationship *made biological sense*, and was a significant improvement on the linear relationship (deltaAIC >2), we accepted the polynomial as the best model. If not, we ran the linear model as the final model. $R^2$ values were calculated for the best model. All $R^2$ values presented here are marginal $R^2$ values, and refer to the proportion of variation explained by only the fixed effects, unless otherwise specified. In addition, slope coefficients were calculated for the linear models. {**This paragraph needs work - polynomial models were rejected if they showed an exponential increase in productivity with climate (e.g. showed GPP increasing exponentially with latitude - needs work on how to word this**}

@@

For the variables which showed a significant interactive or additive effect between MAT and MAP, no other climate variable, in combination with MAT, significantly improved on that model.
